\editone{Stellar convective penetration: parameterized theory and dynamical simulations}

### 2021-10-08 manuscript/ms.tex
small edits per adam/daniel

\begin{equation}
    \editone{
    \tau_{\rm{ff}} = \left(\frac{L_s}{|\alpha| g Q_0}\right)^{1/3},
}
\end{equation}
and the temperature scale of the internal heating over that freefall time $\Delta T$; \editone{mass is nondimensionalized so that the freefall ram pressure $\rho_0(L_s/\tau_{\rm{ff}})^2 = 1$,}
\begin{equation}
\begin{split}
&T^* = (\Delta T)T = Q_0 \tau_{\rm{ff}} T,\qquad
Q^* = Q_0 Q,
\\
&\partial_{t^*} = \tau_{\rm{ff}}^{-1}\partial_t,\,\,\,\,\,
\grad^* = L_s^{-1} \grad,\,\,\,\,\,
p^* = \rho_0 u_{\rm{ff}}^2\varpi,
\\
    &\vec{u}^* = u_{\rm{ff}}\vec{u} = \frac{L_s}{\tau_{\rm{ff}}} \vec{u} = \left(|\alpha| g Q_0 L_s^2\right)^{1/3}\vec{u},\qquad
\\
&k^* = (L_s^2 \tau_{\rm{ff}}^{-1})k,\qquad
\mR = \frac{u_{\rm{ff}} L_s}{\nu},\qquad
\Pran = \frac{\nu}{\chi}.
\end{split}
\end{equation}
For convenience, here we define quantities with $*$ (e.g., $T^*$) as being the ``dimensionful'' quantities of Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq}.
Henceforth, quantities without $*$ (e.g., $T$) are dimensionless.
The dimensionless equations of motion are
\label{sec:simulation_details}
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:nondim_incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\grad \varpi + T \hat{z} + \mR^{-1}\grad^2 \vec{u}
\label{eqn:nondim_momentum} \\
\begin{split}
\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}}  + \grad\dot[-k \grad \overline{T}]\qquad\qquad 
\\
\qquad\qquad\qquad\qquad\qquad= (\Pran\mR)^{-1}\grad^2 T' + Q.
\label{eqn:nondim_temperature}
\end{split}
\end{align}
We construct a domain in the range $z \in [0, L_z]$ and choose $L_z \geq 2$ so that the domain is at least twice as deep as the Schwarzschild-unstable convection zone.
We decompose the temperature field into a time-stationary initial background profile and fluctuations, $T(x, y, z, t) = T_0(z) + T_1(x, y, z, t)$.
$T_0$ is constructed with $\justgrad = \gradad$ for $z \leq L_s$, and $\justgrad = \gradrad$ above $z > L_s$.
We impose a fixed-flux boundary at the bottom of the box ($\partial_z T_1 = 0$ at $z = 0$) and a fixed temperature boundary at the top of the domain ($T_1 = 0$ at $z = L_z$).
We generally impose impenetrable, no-slip boundary conditions at the top and bottom of the box so that $\vec{u} = 0$ at $z = [0, L_z]$.
For a select few simulations, we impose stress-free instead of no-slip boundary conditions ($w = 0$ and $\partial_z u = \partial_z v = 0$ at $z = [0, L_z]$).

@@

\editone{
    In many prior studies, the stiffness has been set by the ratio of the subadiabaticity of $\gradrad$ in the RZ to the superadiabaticity of $\gradrad$ in the CZ,
    \begin{equation}
        \tilde{\mS} = \frac{|\gradrad - \gradad|_{\rm{RZ}}}{|\gradrad - \gradad|_{\rm{CZ}}} = \frac{N^2}{|\gradrad - \gradad|_{\rm{CZ}}}.
    \end{equation}
    In those studies, $\tilde{\mS}$ primarily describes the stratification of the initial state, but it also describes the stratification in superadiabatic boundary layers which drive convection.
    This differs from the case studied here, in that we use an internal heating function which is offset from the boundary to hold the stratification to adiabatic in the CZ once convection develops.
    Previous work has not defined $\mP$, but its definition in our current study should apply to previous studies,
    \begin{equation}
        \mP = -\frac{k_{\rm{CZ}}(\gradrad - \gradad)_{\rm{CZ}}}{k_{\rm{RZ}}(\gradrad - \gradad)_{\rm{RZ}}}.
    \end{equation}
    We note that $\mP$ can be related to $\mS$ and $\tilde{\mS}$, $\mP = (k_{\rm{CZ}}/k_{\rm{RZ}}) \tilde{\mS}^{-1} = (k_{\rm{CZ}}/k_{\rm{RZ}}) (\gradrad - \gradad)_{\rm{CZ}} \mS^{-1}$.
    Our use of internal heating to decouple convective perturbations from $\gradrad$ in the CZ allows us to separately specify these nondimensional parameters.
    The distinction between $\mS$ and $\mP$ is perhaps clearer in the language of stellar evolution, where $\mS$ is roughly the inverse Mach number of the convection while $\mP$ is set by the ratio of $\gradrad$ and $\gradad$.
}

>>>>

\begin{equation}
    \editone{
    \tau_{\rm{ff}} = \left(\frac{L_s}{|\alpha| g Q_0}\right)^{1/3},
}
\end{equation}
and the temperature scale of the internal heating over that freefall time $\Delta T$; \editone{mass is nondimensionalized so that the freefall ram pressure $\rho_0(L_s/\tau_{\rm{ff}})^2 = 1$,}
\begin{equation}
\begin{split}
&T^* = (\Delta T)T = Q_0 \tau_{\rm{ff}} T,\qquad
Q^* = Q_0 Q,
\\
&\partial_{t^*} = \tau_{\rm{ff}}^{-1}\partial_t,\qquad\qquad\qquad\,\,\,
\grad^* = L_s^{-1} \grad,\,\,\,\,\,
\\
    &\vec{u}^* = u_{\rm{ff}}\vec{u} = \frac{L_s}{\tau_{\rm{ff}}} \vec{u}, \qquad\qquad
p^* = \rho_0 u_{\rm{ff}}^2\varpi,
\\
&k^* = (L_s^2 \tau_{\rm{ff}}^{-1})k,\qquad
\mR = \frac{u_{\rm{ff}} L_s}{\nu},\qquad
\Pran = \frac{\nu}{\chi}.
\end{split}
\end{equation}
For convenience, here we define quantities with $*$ (e.g., $T^*$) as being the ``dimensionful'' quantities of Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq}.
Henceforth, quantities without $*$ (e.g., $T$) are dimensionless.
The dimensionless equations of motion are
\label{sec:simulation_details}
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:nondim_incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\grad \varpi + T \hat{z} + \mR^{-1}\grad^2 \vec{u}
\label{eqn:nondim_momentum} \\
\begin{split}
\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}}  + \grad\dot[-k \grad \overline{T}]\qquad\qquad 
\\
\qquad\qquad\qquad\qquad\qquad= (\Pran\mR)^{-1}\grad^2 T' + Q.
\label{eqn:nondim_temperature}
\end{split}
\end{align}
We construct a domain in the range $z \in [0, L_z]$ and choose $L_z \geq 2$ so that the domain is at least twice as deep as the Schwarzschild-unstable convection zone.
We decompose the temperature field into a time-stationary initial background profile and fluctuations, $T(x, y, z, t) = T_0(z) + T_1(x, y, z, t)$.
$T_0$ is constructed with $\justgrad = \gradad$ for $z \leq L_s$, and $\justgrad = \gradrad$ above $z > L_s$.
We impose a fixed-flux boundary at the bottom of the box ($\partial_z T_1 = 0$ at $z = 0$) and a fixed temperature boundary at the top of the domain ($T_1 = 0$ at $z = L_z$).
We generally impose impenetrable, no-slip boundary conditions at the top and bottom of the box so that $\vec{u} = 0$ at $z = [0, L_z]$.
For a select few simulations, we impose stress-free instead of no-slip boundary conditions ($w = 0$ and $\partial_z u = \partial_z v = 0$ at $z = [0, L_z]$).

@@

\editone{
    In many prior studies, the stiffness has been set by the ratio of the subadiabaticity of $\gradrad$ in the RZ to the superadiabaticity of $\gradrad$ in the CZ,
    \begin{equation}
        \tilde{\mS} = \frac{|\gradrad - \gradad|_{\rm{RZ}}}{|\gradrad - \gradad|_{\rm{CZ}}} = \frac{N^2}{|\gradrad - \gradad|_{\rm{CZ}}}.
    \end{equation}
    In those studies, $\tilde{\mS}$ primarily describes the stratification of the initial state, but it also describes the stratification in superadiabatic boundary layers which drive convection.
    In this work, we maintain a nearly adiabatic convection zone without strongly superadiabatic regions by driving convection with an internal heating function which is offset from the lower boundary.
}

\editone{
    Previous work has not defined $\mP$, but its definition in our current study should apply to previous studies,
    \begin{equation}
        \mP = -\frac{k_{\rm{CZ}}(\gradrad - \gradad)_{\rm{CZ}}}{k_{\rm{RZ}}(\gradrad - \gradad)_{\rm{RZ}}}.
    \end{equation}
    We note that $\mP$ can be related to $\mS$ and $\tilde{\mS}$, $\mP = (k_{\rm{CZ}}/k_{\rm{RZ}}) \tilde{\mS}^{-1} = (k_{\rm{CZ}}/k_{\rm{RZ}}) (\gradrad - \gradad)_{\rm{CZ}} \mS^{-1}$.
    Our use of internal heating to decouple convective perturbations from $\gradrad$ in the CZ allows us to separately specify these nondimensional parameters.
    The distinction between $\mS$ and $\mP$ is perhaps clearer in the language of stellar evolution, where $\mS$ is roughly the inverse square Mach number of the convection while $\mP$ is set by the ratio of $\gradrad$ and $\gradad$.
}
